Predicting Ambient Air Pollution (PM2.5) Across the Contiguous U.S.

### 2023-04-22 Draft.Rmd
Update Draft.Rmd

## Models 
```{r Linear}
set.seed(123)
# Fit model and get summary
fit_lm = lm(value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
             log_nei_2008_pm25_sum_10000+log_nei_2008_pm10_sum_10000, data=train)
step <- stepAIC(fit_lm, direction="backward", trace=TRUE)
# Drops county_area, popdens_county, and log_nei_2008_pm25_sum_10000

@@

```{r kNN}
set.seed(123)
# Find ideal k neighbors
sqrt(nrow(train))

>>>>

## Models

```{r Linear}
set.seed(123)
# Fit model and get summary
fit_lm = lm(value ~ CMAQ+lat+county_area+lon+aod+popdens_county+zcta+
             log_nei_2008_pm25_sum_10000+log_nei_2008_pm10_sum_10000, data=train)
step <- stepAIC(fit_lm, direction="backward", trace=TRUE)
# Drops county_area, popdens_county, and log_nei_2008_pm25_sum_10000

@@

```{r kNN ALL MODELS FAILED}
set.seed(123)
# Find ideal k neighbors
sqrt(nrow(train))
